On the goodness-of-fit of an exponential random graph model to a social network sample

### 2021-01-20 Manuscript/manuscript.tex
Updated Table

\documentclass[a4paper, man]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{apacite}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\thispagestyle{empty}
\maketitle
\pagenumbering{arabic}

@@

The complexity factor is finally examined by varying the complexity of the exponential random graph model (ERGM) that is applied to the different network samples. Note that a complexity continuum has already defined by way of the network samples which vary in their size and heterogeneity. ERGMs with low, moderate, and high respective complexity are fitted to each of these different samples. As such, with regards to the heterogeneity factor, three different scenario's are identified. It is consequently examined whether the precision of the meta-analyzed ERGM increases for a decrease in the discrepancy between sample and model complexity. It is also assessed whether this is consistent with the goodness-of-fit (GOF) indices. Furthermore, both covariate and structural effects are included in each ERGM, which remain constant regardless of the complexity of the sample to which the ERGM is applied. This enables examining whether covariate parameters estimates are more precise than their structural counterparts. \clearpage \noindent Ultimately, for the scenario's as they have been defined here, a total of $27$  scenario's can be identified. Under these specifications, the effects for all the hypothesized factors can be evaluated.

>>>>

\documentclass[a4paper, man, floatsintext]{apa6}

\usepackage[utf8x]{inputenc}
\usepackage{booktabs}
\usepackage{apacite}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\maketitle

@@

The complexity factor is finally examined by varying the complexity of the exponential random graph model (ERGM) that is applied to the different network samples. Note that a complexity continuum has already defined by way of the network samples which vary in their size and heterogeneity. ERGMs with low, moderate, and high respective complexity are fitted to each of these different samples. As such, with regards to the heterogeneity factor, three different scenario's are identified. It is consequently examined whether the precision of the meta-analyzed ERGM increases for a decrease in the discrepancy between sample and model complexity. It is also assessed whether this is consistent with the goodness-of-fit (GOF) indices. Furthermore, both covariate and structural effects are included in each ERGM, which remain constant regardless of the complexity of the sample to which the ERGM is applied. This enables examining whether covariate parameters estimates are more precise than their structural counterparts. \clearpage \noindent The reader is referred to table 1 for a more concise overview of the set-up of the simulation study. As becomes apparent from the table, in total $27$  simulation scenario's can be be identified.
\linebreak
\begin{table}[!h]
\caption{Simulation study set-up}
\begin{tabular}{@{}ll|lll@{}}
\toprule
           &               & \multicolumn{3}{l}{Sample size}         \\ \midrule
Complexity & Heterogeneity & 10          & 20          & 50          \\ \midrule
Low        & Low           & Scenario 1  & Scenario 2  & Scenario 3  \\
           & Moderate      & Scenario 4  & Scenario 5  & Scenario 6  \\
           & High          & Scenario 7  & Scenario 8  & Scenario 9  \\
Moderate   & Low           & Scenario 10 & Scenario 11 & Scenario 12 \\
           & Moderate      & Scenario 13 & Scenario 14 & Scenario 15 \\
           & High          & Scenario 16 & Scenario 17 & Scenario 18 \\
High       & Low           & Scenario 19 & Scenario 20 & Scenario 21 \\
           & Moderate      & Scenario 22 & Scenario 23 & Scenario 24 \\
           & High          & Scenario 25 & Scenario 26 & Scenario 27 \\ \bottomrule
\end{tabular}
\end{table}
